---
title: "Survey Results Investigation"
author: "abc & def"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
format:
  html:
    toc: true
    code-fold: true
    theme: cosmo
---

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
```

## Introduction

This report demonstrates a simple example of a data analysis workflow using **Quarto**.  
We’ll explore a small dataset of survey results.

The dataset includes three columns:

- `id` – respondent ID  
- `age` – age of the respondent  
- `score` – satisfaction score (0–100)


## Load and inspect the data

```{r}
data <- read.csv("../data/raw/survey_results.csv")
head(data)
summary(data)
```


## Clean the data

```{r}
# Remove missing values (if any)
clean_data <- na.omit(data)
```


## Summary Statistics

```{r}
summary(clean_data$score)
mean_score <- mean(clean_data$score)
sd_score <- sd(clean_data$score)

paste("Average score:", round(mean_score, 1))
paste("Standard deviation:", round(sd_score, 1))
```


## Visualize the data

```{r}
ggplot(clean_data, aes(x = age, y = score)) +
  geom_point(color = "blue", size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "purple") +
  theme_minimal() +
  labs(title = "Survey Score by Age",
       x = "Age",
       y = "Score")
```


## Conclusions

- The average score is around **`r round(mean_score, 1)`**.
- There appears to be a slight relationship between age and score.  
- Further analysis could include correlation testing or regression modeling.

